The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-03 paper/ms.tex
proofread

Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citet{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for the~31 giants for which oscillations are detected with sufficient signal-to-noise. These parameters are listed in Table~\ref{rgs}; the stars are noted as showing `RG' variability in Table~\ref{table_all}, whereas this field is left blank for stars of luminosity class III for which oscillations are not unambiguously detected. High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars valuable as benchmarks for large spectroscopic surveys or testing detailed stellar models. This sample will be a valuable addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.

@@

% tess halo 
The halo method naturally extends to other contexts where simple aperture photometry is not possible, such as for saturated stars observed by the Transiting Exoplanet Survey Satellite \citep[TESS;][]{tess}. Although the saturation limit is brighter ($T_{mag} \sim 6$) and this problem accordingly affects fewer stars and less badly, there are stars such as $\alpha$~Centauri and $\beta$~Hydri where the bleed column reaches the edge of the chip and a SAP light curve is irrecoverable. We expect that TV-min halo photometry will therefore be valuable in ensuring that TESS can observe the very brightest stars.

>>>>

Using the Sydney pipeline \citep{Huber2009} with modifications to the extraction of \Dnu detailed in \citet{Yu2018}, we extract the global asteroseismic parameters \numax and \Dnu for the~31 giants for which oscillations are detected with sufficient signal-to-noise. These parameters are listed in Table~\ref{rgs}; the stars are noted as showing `RG' variability in Table~\ref{table_all}, whereas this field is left blank for stars of luminosity class III for which oscillations are not unambiguously detected. High precision spectroscopy of these stars would permit detailed stellar modelling and the extraction of precise elemental abundances, which would make these stars useful as benchmarks for large spectroscopic surveys or testing detailed stellar models. This sample will be an addition to the~36 Gaia FGK benchmark stars \citep{gaiabenchmark1,gaiabenchmark3,2018RNAAS...2c.152J}, the 23 BRITE-Constellation asteroseismic giants \citep{Kallinger2019}, and the~33 \kepler Smear Campaign spectroscopic benchmark red giants \citep{smearcampaign}.

@@

% tess halo 
The halo method naturally extends to other contexts where simple aperture photometry is not possible, such as for saturated stars observed by the Transiting Exoplanet Survey Satellite \citep[TESS;][]{tess}. Although the saturation limit is brighter ($T_{mag} \sim 6$) and this problem accordingly affects fewer stars and less badly, there are stars such as $\alpha$~Centauri and $\beta$~Hydri where the bleed column reaches the edge of the chip and a SAP light curve is irrecoverable. We expect that TV-min halo photometry will therefore be important in ensuring that TESS can observe the very brightest stars.
